The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-09-29 paper.tex
Additions
Added a sentence on typical switching times in Section 3.3, and added a
new section on quantum state engineering using MZ interferometers.

Unlike polarisation or dual-rail encoding, time-bin encoding does not lend itself to `native' single-qubit operations. Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding. An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}. Another promising advance is an ultrafast measurement technique for time bins based on converting into frequency bins \cite{bib:Donohue2013}. Scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}. This is discussed in more detail in Section \ref{sec:timebins}.

@@

>>>>

Unlike polarisation or dual-rail encoding, time-bin encoding does not lend itself to `native' single-qubit operations. Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding. \sihui{Typical switch times that can be achieved are in the picoseconds range \cite{bib:Dietrich16}.} An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}. Another promising advance is an ultrafast measurement technique for time bins based on converting into frequency bins \cite{bib:Donohue2013}. Scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}. This is discussed in more detail in Section \ref{sec:timebins}.

@@

\sihui{
\section{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
}
